---
title: "Stack Overflow Analysis"
author: ""
date: "2016年10月11日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 2016 Stack Overflow Survey data analysis

## 1. Explore and clean the dataset
```{r}
data <- read.csv("./Stack Overflow Survey Response/2016 Stack Overflow Survey Responses.csv")
View(data)
#str(data)
data.summary <- summary(data)
View(data.summary)
summary(data[,"collector"])
summary(data[,"country"])
table(data[,"so_region"])
table(data[,"age_range"])

# delete the missing age_midpoint data, salary_midpoint data
data.clear <- data[complete.cases(data[,c("age_midpoint","salary_midpoint")]),]

# Next we just make the category data (salary) to continuous data by adding some noise term( Normal distribution with the standard deviation 10)
data.clear["salary_norm"] <- data.clear[,"salary_midpoint"] + runif(nrow(data.clear),0,1)*5000
```
From the summary table, we can see that there are 56030 observations and 66 variables for the survey.

For the collectors: there are six collectors: Facebook, House ads, Meta Stack Overflow Post, Miscellaneous, Reddit, and Twitter.

For the age-range, we saw that there are 303 observations don't have age, so we need to delete these dirty data.





```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
