---
title: "Stack Overflow Analysis"
author: "Group 8"
date: "11 October, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(ggplot2)
library(plyr)
library(reshape2)
```


# 2016 Stack Overflow Survey data analysis

<<<<<<< HEAD
## 1. Explore and clean the dataset
```{r}
data <- read.csv("./Stack Overflow Survey Response/2016 Stack Overflow Survey Responses.csv")
View(data)
#str(data)
data.summary <- summary(data)
View(data.summary)
summary(data[,"collector"])
summary(data[,"country"])
table(data[,"so_region"])
table(data[,"age_range"])

# delete the missing age_midpoint data, salary_midpoint data
data.clear <- data[complete.cases(data[,c("age_midpoint","salary_midpoint")]),]

# Next we just make the category data (salary) to continuous data by adding some noise term(Normal distribution with the standard deviation 10)
data.clear["salary_norm"] <- data.clear[,"salary_midpoint"] + runif(nrow(data.clear),0,1)*5000

# delete the data which has no specific gende
data.clear <- data.clear[(data.clear[,"gender"] == "Male") | (data.clear[,"gender"] == "Female") ,]

```
From the summary table, we can see that there are 56,030 observations and 66 variables for the survey.

For the collectors: there are six collectors: Facebook, House ads, Meta Stack Overflow Post, Miscellaneous, Reddit, and Twitter.

For the age-range: we saw that there are 303 observations don't have age, so we need to delete these dirty data.





# Dinan can do some descriptions for the dataset here.












# 2. Descriptive statistives analysis for the dataset

## 2.1 The occpupation
### 2.1.1 Describe the proportion of different occupation
```{r}
ggplot(data.clear,aes(x = occupation)) +geom_bar(position = "dodge") + theme(axis.text.x = element_text(angle = 45,colour = "black",size=13,hjust=1))

ggplot(data.clear,aes(x = occupation, fill = gender)) +geom_bar(position = "dodge") + theme(axis.text.x = element_text(angle = 45,colour = "black",size=13,hjust=1))

```

From the barchart, we can conclude that more respondents consider themself Full-stack developers than any other roles. The second largest one is back-end web developers, and the third one is students. The smallest one is mobile developer - Windows Phone, which may be due to the market shares of Windows Phone is a little. From the second barchart, we find that the numbers of male developers is much larger than that of female developers.

### 2.1.2 What is the salary differene for different occupation developers?
```{r}
occupation.salary <- ddply(data.clear, "occupation", function(x) mean(x[,"salary_midpoint"]))  # calculate the average salaries for different occupations
names(occupation.salary)[2] <- "average_salary"  # rename the column names

#View(occupation.salary)
ggplot(occupation.salary) + geom_bar(aes(x = reorder(occupation,average_salary), y = average_salary), stat = "identity", position = "dodge")+ theme(axis.text.x = element_text(angle = 45,colour = "black",size=13,hjust=1)) 

```

From the barchart, we conclude that the engineering manager and Executive(VP oF Eng., CTO, CIO, etc) have the highest average salary, which is above 100,000 dollars. Most of the other occupation developers' average salaries are around 50,000 dollars. And the student developers have the lowest average salaries, just 12,500 dollars.

### 2.1.3 How about the gender propertion and average salaries of different occupation developers?
```{r}
occupation.gender.salary <- ddply(data.clear, .(occupation,gender), function(x) mean(x[,"salary_midpoint"]))  # calculate the average salaries for different occupations

#View(occupation.gender.salary)
names(occupation.gender.salary)[3] <- "average_salary"  # rename the column names
ggplot(occupation.gender.salary) + geom_bar(aes(x = reorder(occupation,average_salary), y = average_salary, fill = gender), stat = "identity", position = "dodge")+ theme(axis.text.x = element_text(angle = 45,colour = "black",size=13,hjust=1))

```

From barchart, we conclude that for most occupations, there are not so much differences for salaries. So there are no discrimination for developers on salaries.

### 2.1.4 Do category test to decide for male and female developers, if it has different proportation for different occupation.
```{r}
# using cast function to make the long-to-wide format data
occupation.gender.salary.cast <- dcast(occupation.gender.salary, gender ~ occupation)
View(occupation.gender.salary.cast)

# substitute NA value to 0
occupation.gender.salary.cast[is.na(occupation.gender.salary.cast)] <- 0

# Proportion test prepartion
#change data from dataframe to matrix
occupation.gender.salary.cast.matrix <- data.matrix(occupation.gender.salary.cast)
colnames(occupation.gender.salary.cast.matrix)[29] <- "System_administrator"  #change column names
View(occupation.gender.salary.cast.matrix)
chitest.data <- subset(occupation.gender.salary.cast.matrix, select = Analyst:(System_administrator))
chisq.test(chitest.data)

```

From chisq test, we got that the p-value is much smaller than 0.05, so we reject the Non Hyphothesis, which means ......
# ??????#














=======
# 3. Correlation Analysis

## Correlation test on different variables with "salary_midpoint":

Based on the survey from Stack Overflow, we want to do an analysis on the salary distribution and find a linear model who describes this variable through other independ variables. The first variable we want to include in our analysis is gender. We want to see if there is a significant difference in the salary distribution when looking at gender.

```{r}
summary(data.clear[,"gender"])

#Number of female/male
summary(data.clear[,"gender2"] == "Female") #3202 female
summary(data.clear[,"gender2"] == "Male") #51388 male

# Salary by gender
ggplot(data=data.clear) + geom_boxplot(aes(gender, salary_midpoint))

# T-test on gender and salary
t.test(data.clear[data.clear[,"gender2"]=="Female", "salary_midpoint"], data.clear[data.clear[,"gender2"]=="Male", "salary_midpoint"], alternative = "two.sided")

```

The dataset only include 3202 women, compared to 51388 men. This might interfere with our results. The boxplot looks almost the same for both gender, and after running a t-test we cannot say that there is a significant difference in the two means.

## Correlation test among different variables with "salary_midpoint"

Other variables we find interesting is age, the Big Mac index, IT and programming experience and programming ability. We will use correlation tests and linear regression to see how these independent variables will relate to salary.

We would expect the salary to increase with age, and therefore we add age as an independent variable in our model. The big mac index shows the average price of a Big Mac in a country, and this index is sometimes used to describe the purchasing power parity in a country. We expect that respondents from countries with a high Big Mac score also have higher wages.  

Since this survey is mainly answered by people using Stack Overflow, we would expect some of the respondents having jobs where coding is a part of their job. Therefore, we want to include programming ability to see if this will have a significant impact on salary. We also want to include IT and programming experience, and we believe that more experience will result in a higher salary.

```{r}
cor.test(data.clear[, "salary_midpoint"], data.clear[, "age_midpoint"])
cor.test(data.clear[, "salary_midpoint"], data.clear[, "programming_ability"])
cor.test(data.clear[, "salary_midpoint"], data.clear[, "experience_midpoint"])
cor.test(data.clear[, "salary_midpoint"], data.clear[, "big_mac_index"])

```

Based on the correlation test, it could be observed that salary has a relatively strong positive relationship with age, programming ability, experience, and the big mac index. The big mac index has the highest correlation with salary, which indicates that the salary level is strongly positive related to the consumption level of one area. Furthermore, the working experience demonstrates high positive correlation with salary as well. This shows that working experience has a huge impact on the salary level.

## Single Variable Linear Regression Test with "salary_midpoint" as the dependent variable
```{r}
# Detect the linear relationship between salary and the big mac index as it shows strong positive correlation with salary
model1 <- lm(salary_midpoint ~ big_mac_index, data = data.clear)
summary(model1)

# Detect the linear relationship between salary and working experience as it shows strong positive correlation with salary
model2 <- lm(salary_midpoint ~ experience_midpoint, data = data.clear)
summary(model2)

# Detect the linear relationship between salary and programming ability as it shows strong positive correlation with salary
model3 <- lm(salary_midpoint ~ programming_ability, data = data.clear)
summary(model3)

# Detect the linear relationship between salary and age as it shows strong positive correlation with salary
model4 <- lm(salary_midpoint ~ age_midpoint, data = data.clear)
summary(model4)
```

Based on the above analysis, it could be observed that these four variables all have certain linear relationship with salary, which could contribute to the further investigation on multi-variables linear relationship with salary

## Multiple Variables Linear Regression Test with "salary_midpoint" as the dependent variable
```{r}
model5 <- lm(salary_midpoint~ experience_midpoint + big_mac_index + age_midpoint + programming_ability, data = data.clear)
summary(model5)

model6 <- lm(salary_midpoint~ experience_midpoint + gender + big_mac_index + age_midpoint + programming_ability, data = data.clear)
summary(model6)

```

In our model we get an adjusted R-squared equal to 0.4493, which means that 44.93% of the salary variable is described in this model. All the dependent variables are significant at the 1% level, except for gender which is significant at the 5% level. 

The intercept tells us what the salary will be if all our independent variables are zero. This number is negative and does not give us any valuable information without combining it with more variables. If we look at the age variable we can see that by increasing age by one year, salary will increase by 1140 dollars. The estimate of experience tells us that one more year of experience will increase salary by 2010 dollars. 

Of the beta estimates we see that the Big Mac index has the biggest impact on salary. When the Big Mac price of a country increase by 1 dollar, we will expect the salary to respondents from this country to increase by 16 700 dollars. 

If the respondent’s ability in programming increase by one on a scale from 1 to 10, the salary will increase by 3885 dollars. The gender variable does not have a big influence on salary in this model, but from this sample the model indicates that men tends to have lower salary than women.  


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
