---
title: "Stack Overflow Analysis"
author: ""
date: "11 October, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 2016 Stack Overflow Survey data analysis

<<<<<<< HEAD
## 1. Explore and clean the dataset
```{r}
data <- read.csv("./Stack Overflow Survey Response/2016 Stack Overflow Survey Responses.csv")
View(data)
#str(data)
data.summary <- summary(data)
View(data.summary)
summary(data[,"collector"])
summary(data[,"country"])
table(data[,"so_region"])
table(data[,"age_range"])

# delete the missing age_midpoint data, salary_midpoint data
data.clear <- data[complete.cases(data[,c("age_midpoint","salary_midpoint")]),]

# Next we just make the category data (salary) to continuous data by adding some noise term( Normal distribution with the standard deviation 10)
data.clear["salary_norm"] <- data.clear[,"salary_midpoint"] + runif(nrow(data.clear),0,1)*5000
```
From the summary table, we can see that there are 56030 observations and 66 variables for the survey.

For the collectors: there are six collectors: Facebook, House ads, Meta Stack Overflow Post, Miscellaneous, Reddit, and Twitter.

For the age-range, we saw that there are 303 observations don't have age, so we need to delete these dirty data.
=======
Correlation Calculation with different varialbes with "salary_midpoint":
>>>>>>> 86e56dbf5972ab96985b972ff099b871fb957576

```{r, echo=FALSE}
summary(Stack[,"gender"])

#fixed gender
Stack[,"gender2"] <- NA
for (i in 1:nrow(Stack)){
  if (Stack[i,"gender"] == "Female") Stack[i,"gender2"] <- "Female"
  if (Stack[i,"gender"] == "Male") Stack[i,"gender2"] <- "Male"
}

library(ggplot2)
#Number of female/male
summary(Stack[,"gender2"] == "Female") #3202 female
summary(Stack[,"gender2"] == "Male") #51388 male

# Salary by gender
ggplot(data=Stack) + geom_boxplot(aes(gender2, salary_midpoint))

# T-test on gender and salary
t.test(Stack[Stack[,"gender2"]=="Female", "salary_midpoint"], Stack[Stack[,"gender2"]=="Male", "salary_midpoint"], alternative = "two.sided")

# Correlation test among different variables with "salary_midpoint"
cor.test(stack[, "salary_midpoint"], stack[, "age_midpoint"])
cor.test(stack[, "salary_midpoint"], stack[, "programming_ability"])
cor.test(stack[, "salary_midpoint"], stack[, "experience_midpoint"])
cor.test(stack[, "salary_midpoint"], stack[, "big_mac_index"])

lm2 <- lm(salary_midpoint~ experience_midpoint + gender2 + big_mac_index + age_midpoint + programming_ability, data = Stack)
summary(lm2)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
