---
title: "Group 8 Maths and Stats Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Introduction
Business environment in China is unique. Multinational companies (MNC) often find it difficult to compete with local companies.  

China is a country where the government has a relatively strong interception and interference on its economy. Thus, state-owned companies in China may have a stronger relationship with the government and be affected more by the government compared with other kinds of companies.

A stronger connection with the government may benefit the company with easy access to important information, such as big news or change of policies. It could benefit the company with prior gain of resources as well, such as controlled materials. Moreover, one state-owned company could operate more easily with relatively low risk of bankruptcy due to the help offered by the government.

Based on the above information and analysis, it may be interpreted that the relationship between the company-related factors and the government-related factors of one state-owned company should be stronger than that of other kinds of companies.

This report analyse replication dataset provided by Zhu (2016) that consisted of information about different companies in 30 provinces in China. The relationship between variables that affect company revenue will be investigated using correlation test and other different statistical testing. Then, we will examine the significant variables using linear regression to calculate their impact to the log of company revenue.

# 2. Theory
The theory we have based our analysis on is a paper published in 2012 about political connections and how this affects a firm's performance. 

Companies with a strong relationship to the government benefit from easier access to government-related resources and bureaucratic processes, however, research conducted on this relationship with companies' financial performance is varied. In China, 76 out of 98 companies in 2014 Fortune 500 list, are state-owned (Cendrowski, 2015) and it shows the importance of government of China in the development of these companies.

One of the theories on this topic is from Pfeiffer and Salancik (1978), they developed a theory stating that political connections will increase a firms value. Another theory, published by Jensen and Meckling (1976), argue that a firm which have a CEO with strong government connections might utilize this benefit in his own interests rather than the business' interest. We found these theories quite interesting and wanted to see if we could find any support for them in our data.

# 3. Methods
The analysis is conducted using several statistical tools in R, i.e. statistical test and linear modelling. Some libraries such as `ggplot2`, `scales` and `stargazer` are loaded to the console to visualise the data.
```{r library, results='hide'}
library(ggplot2)
library(scales)
library(plyr)
```

## 3.1 Description

```{r, results='hide'}
load("/Users/XINWEI_LI/Desktop/Math & Statistics Foundations/MSF_Team_8/ForeighPresenceChina -- finally chosen/ForeignPresence&ETCs.RData")
mnc <- as.data.frame(x)
ls.str(mnc)
summary(mnc)
```

The dataset contains 40 variables and 11360 observations. The data covered 11360 different companies observed across 30 provinces in China out of a total of 276,474 companies recorded in 2004 by National Bureau of Statistics of China (2014). The variables are divided into three groups, i.e. firm-level variables, industry-level variables and province-level variables. Firm-level variables consist of the properties of each firm, which include the type of ownership, revenue, number of employees and several variables that highlight the relationship between a firm and the government of China in 2004. Industry-level variables illustrate the scale of the industry and the market share of different groups of companies, including foreign firms and the industry leaders. They also try to highlight the amount of government influence by measuring the linear combination of the amount of help received by government officials, as well as the median of tax rate incurred by each firm in the industry. Lastly, province-level variables indicate the macroeconomic information regarding a province, such as its GDP per capita and the level of MNC activities in the region (e.g. foreign direct investments and trades). Below are the details of each variable analysed in this report.

### 3.1.1 Firm-Level Variables
|Variable|Description|
|:------------|:------------------------------------------------|
|`idstd`|Company ID|
|`lectcs`|Log of firm expenditures on entertainment as a percentage of annual revenue.|
|`soe`|Whether a firm is state-owned or not. (1 = Yes, 0 = No)|
|`collective`|Whether a firm is collectively-owned. (1 = Yes, 0 = No)|
|`private`|Whether a firm is privately-owned. (1 = Yes, 0 = No)|
|`foreign_HMT`|Whether a firm is owned by foreign owner from Hong Kong, Macao or Taiwan.|
|`foreign_NonHMT`|Whether a firm is owned by foreign owner other not from Hong Kong, Macao or Taiwan.|
|`mixedown`|Other firms not identified in `soe`, `collective`, `private`, `foreign_HMT` and `foreign_NonHMT` are coded 1.|
|`revenue`|Total revenue in 2004 in log form|
|`lemp`|Total number of employee in 2004 in log form|
|`sales_otherprov`|Whether a firm sells to other provinces. (1 = Yes, 0 = No)|
|`govtsales`|Proportion of revenue from transactions with the government|
|`soesales`|Proportion of revenue from transactions with state-owned enterprises|
|`relationship`|Years of relationships between the firm and its main clients|
|`licenses`|Number of licenses required to operate|
|`lceopay`|CEO annual salary in log form|
|`interaction`|Number of days of interactions with the government|
|`gm_govt`|Whether the general manager is appointed by the government. (1 = Yes, 0 = No)|

### 3.1.2 Industry-Level Variables
|Variable|Description|
|:------------|:------------------------------------------------|
|`foreign_output`|The share of output by foreign-owned firms|
|`HMT_output`|Percentage output by firms owned by shareholders from Hong Kong, Macao or Taiwan|
|`NonHMT_output`|Percentage output by firms owned by other foreign nationals|
|`w_con_pdc4`|Market share of four biggest firms in the industry|
|`w_con_pdc8`|Market share of eight biggest firms in the industry|
|`marketsize`|The market size of the industry|
|`growthrate`|Output growth 2001-2003|
|`last_intensity`|the ratio of fixed asset per number of employees in log form|
|`lscale`|The mean of the size of firms that has 50% of industry market share in log form|
|`mgovthelp`|A linear combination of government helpfullness based on the contribution of government officials|
|`mtaxrate`|Median of firms tax paid divided by total revenue|
|`prov_ind`|Industry ID by Province|

### 3.1.3 Province-Level Variables
|Variable|Description|
|:------------ |:------------------------------------------------|
|`MNC`|Principal factor analysis of FDI inflow and MNC trades in a province.|
|`lwdist`|Geographic distance|
|`lgdpper2003`|Log of GDP per capita of the province in 2003|
|`gdp2003`|GDP in 2003|
|`lpop2003`|Log of the province's population in 2003|
|`province`|The name of the province|
|`provinceID`|Province ID|

## 3.2. Strength and Limitations
This dataset represent the ties between firms and the government of China. Given the unique feature of Chinese industry that most of big firms in China are state-owned, as of 98 companies in 2014 Fortune 500, 76 of them are state-owned (Cendrowski, 2015), this dataset would highlight how strong the relationship with the goverment affect the CEO salary of a company or the company revenue. 

However, the dataset possess some limitations. Although industry ID numbers are provided, the sector was not clearly specified in the dataset or in previous publications. Moreover, the same industry in different provinces were coded differently, thus, the impact of a specific industry could not be measured. 

# 4. Analysis
## 4.1 Statistics Description of the Dataset 
### 4.1.1 Exploring Province-level Variables

Provinces variable were separated from the datasets. Before the data was plotted, `province` variable needed to be converted to factor. The summary showed the sample of each province ranges between 85 (Xinjiang) and 846 (Shangdong).

```{r, tidy=TRUE}
mnc$province <- as.factor(mnc$province)
summary(as.factor(mnc$province))

# Plot the numbers of samples of different provinces
ggplot(mnc) + geom_bar(aes(x = as.factor(province)))+ theme(axis.text.x = element_text(angle = 45,colour = "black",size=13,hjust=1))

#Get the data for province
mnc.prov <- as.data.frame(mnc[!duplicated(x[,"province"]),])

#Plot the GDP of different provinces
ggplot(mnc.prov) + geom_bar(aes(x = as.factor(province), y = gdp2003),stat = "identity", position = "dodge") + theme(axis.text.x = element_text(angle = 45,colour = "black",size=13,hjust=1))
```

The GDP in 2003 were plotted in a barchart. The first highest three GDP provinces are Guangdong, Jiangsu and Shandong. The lowest three GDP provinces are Qinghai, Ningxia and Hainan. Then, we visualised the relationship between provinces' number of population (log) and their log of GDP per capita.

```{r}
ggplot(data=mnc) + geom_boxplot(aes(as.factor(province), revenue)) + theme(axis.text.x = element_text(angle = 45,colour = "black",size=13,hjust=1))
```

It can be concluded that the Shanghai firms' revenues have the largest interval and Jiangxi has the smallest revenues interval. The median revenues in Shanghai is highest and that in Qinghai is the lowest.

# MORE CONCLUSION --- Elaine

### 4.1.2 Exploring GDP-related Variables

```{r, message = FALSE}
cor.test(mnc.prov[,"lpop2003"], mnc.prov[,"lgdpper2003"])

```

There is no strong relationship between the population and capital. From the correlation test result, we found that the p-value is 0.4043, which is much larger than 0.05, so we cannot reject the Null Hypothesis at a 95% confindence level. Therefore, there is no strong correlation between these two variables. The next part explore the link between provinces' size and their GDP per Capita.

```{r}
cor.test(mnc.prov[,"lwdist"], mnc.prov[,"lgdpper2003"])

```

The weighted geographic distance and GDP per Capita do not show any significant relationship. The p value is 0.3297, which is much larger than 0.05, thus, the Null Hypothesis cannot be rejected. Although there is no strong correlation, these two variables are positive correlated, which means large province enjoyed slightly more GDP per Capita.

### 4.1.3 T-test of Company Revenue for Beijing and Shanghai
```{r}
t.test(mnc[mnc[,"province"] == "Beijing","revenue"],mnc[mnc[,"province"] == "Shanghai","revenue"], alternative = "two.sided")
```

We conducted T-test of revenue for Beijing and Shanghai, two biggest cities in China. The p value is 0.1419, which is larger than 0.05, so we can not reject the Null Hypothesis on a 95 % confidence level. We can not find a significant difference in the two means.

### 4.1.4. Description of the Firms Ownership 

```{r, echo = FALSE}
# Making a new column including all the different ownerships
mnc[,"ownership"] <- NA
for (j in 1:nrow(mnc)){
  if (mnc[j,"soe"] == 1) mnc[j,"ownership"] <- "state"
  if (mnc[j,"collective"] == 1) mnc[j,"ownership"] <- "collective"
  if (mnc[j,"private"] == 1) mnc[j,"ownership"] <- "private"
  if (mnc[j,"foreign_HMT"] == 1) mnc[j,"ownership"] <- "foreign_HMT"
  if (mnc[j,"foreign_NonHMT"] == 1) mnc[j,"ownership"] <- "foreign_NonHMT"
  if (mnc[j,"mixedown"] == 1) mnc[j,"ownership"] <- "mixed"
}

ggplot(data=mnc) + geom_bar(aes(ownership))
```

#### Average Revenue of Each Ownership
```{r}
mean(mnc[mnc[,"ownership"]=="state", "revenue"])
mean(mnc[mnc[,"ownership"]=="collective", "revenue"])
mean(mnc[mnc[,"ownership"]=="private", "revenue"])
mean(mnc[mnc[,"ownership"]=="foreign_HMT", "revenue"])
mean(mnc[mnc[,"ownership"]=="foreign_NonHMT", "revenue"])

ggplot(data=mnc) + geom_boxplot(aes(ownership, revenue, fill = ownership))
```

As we can see of the barplot there is a lot of companies in the bar with "mixed" ownership compared to the other categories. Therefore it might be difficult to do any valuable analysis on this data. If we look at the boxplot we can see that it looks like the distribution of revenue might be different between the different kind of ownership.

## 4.2 Correlation Analysis

### 4.2.1 Correlation Test among Different Variables with "`lemp` (log of total employees in 2004)"

```{r, message=FALSE}
ggplot(mnc) + geom_point(aes(lemp,revenue))
cor.test(mnc[,"lemp"],mnc[,"revenue"])

cor.test(mnc[,"lemp"],mnc[,"lceopay"])

cor.test(mnc[,"lemp"],mnc[,"letcs"])
```

From the scatter diagram, we can find that the with the increasement of the firm's total employees, the total income and CEO payment will increase. But the log of firm expenditure on entertainment and travel cost as % of total revenue will seem to decrease when firm's total employees increases. From the correlation test, we get that the correlation between lemp and revenue, lceopay and letcs are 0.79, 0.34, and -0.10.

### 4.2.2 Correlation Test among Different Variables with "`Revenue` (log of total business income)"
#### 4.2.2.1 Correlation Test with Government Relative Factors
According to the dataset provided, we would like to examine the correlation of all factors relative to the government with the revenue of the company.
In this case, we analysis the factors:

1. Help from the government: based on the condition in China, we think with more help from the government, one company may perform better and gain more revenue.

2. Proportion of sales to the government: we think this factor could help to increase the revenue as sales to Chinese government meaning stable sales with only low risk

3. Interaction with the government: we add this factor because with more time working on the government assignments and communications, it would be easier for the company to know news and policies from the goverment and act accordingly and timely.

```{r, tidy = TRUE}
cor.test(mnc[, "revenue"], mnc[, "mgovthelp"])

cor.test(mnc[, "revenue"], mnc[, "govtsales"])

cor.test(mnc[, "revenue"], mnc[, "interaction"])

```

Based on the correlation tests, it could be observed that the total business income of one company has a quite weak connection with the factors relative to the government, containing even negative correlation with some of the factors. In this case, the theory mentioned previously could not be proved since we hardly observe any strong positive or negative correlation among governmental factors with the performance of a company. Furthermore, the factors tested above may not be used as the independent variables for the linear regression model with the revenue as the dependent variables.

#### 4.2.2.2 Correlation Test with Non-government Relative Factors
Based on the above tests, government relative factors have very weak impacts on the revenue of the company. In this case, many other non-government relative factors should be examined for better interpretation of the dataset and smothier linear regression test.
The factors are to be analyzed are:

1. GDP per capita in 2003: due to the fact that the GDP of one country may have big impact on the performance of companies in that country, this factor is added for correlation test.

2. Market size: the revenue of one company may fluctuate according to the market size, thus this factor is examined.

3. Output growth rate: we add this factor because we think the change of the output growth rate may affect the revenue as there exists some direct relationship between them.

4. Relationship with clients and suppliers: since a good and long existing relationship with the clients and suppliers could help with the increase of the revenue, we would like to test this factor and see its correlation with the revenue.

5. Licenses: we think this factor has some correlation with the revenue as more licenses one company holds, it would be possible for that company to generate more revenue.

6. CEO annual income: we think the performance of the company's CEO largely affect the revenue that company earns. Thus, we examined this factor to observe the correlation.

# REMEBER!!! --- Elaine
7. letcs:

```{r, tidy = TRUE}
cor.test(mnc[, "revenue"], mnc[, "lgdpper2003"])

cor.test(mnc[, "revenue"], mnc[, "marketsize"])

cor.test(mnc[, "revenue"], mnc[, "growthrate"])

cor.test(mnc[, "revenue"], mnc[, "relationship"])

cor.test(mnc[, "revenue"], mnc[, "licenses"])

cor.test(mnc[, "revenue"], mnc[, "lceopay"])
ggplot(data = mnc, aes(x = lceopay, y = revenue)) + geom_point()

cor.test(mnc[, "revenue"], mnc[, "letcs"])
ggplot(data = mnc, aes(x = letcs, y = revenue)) + geom_point()
```

Based on the correlation tests, it could be observed that the total business income of one company has a positive connection with all the factors mentioned above except the output growth rate (with -0.053 correlation with revenue). The correlation with revenue in descending order is: CEO annual income (0.493), market size (0.306), relationship with clients and suppliers (0.275), GDP per capita in 2003 (0.237) and licenses (0.128). blablabla

## 4.3 Linear Regression
### 4.3.2. Single Variable Linear Regression Test with `Revenue` as the Dependent Variable

Based on our correlation analysis we want to look deeper into the variables which had the highest correlation with revenue. 

#### 4.3.2.1 `lgdpper2003` (GDP per capita in 2003 (log)) as the Independent Variable
```{r, echo=FALSE}
rev_gdp <- lm(revenue ~ lgdpper2003, data = mnc)
summary(rev_gdp)

```
The log of GDP per capita in 2003 (lgdpper2003) has a positive inpact on revenue. By increasing the GDP per capita with 1 %, revenue will increase by approximately 1 %. The p-value is less than 0.05 and is significant on a 5% level, and the revenue variable is described by 5.6 % in this model.

#### 4.3.2.2. `marketsize` (Market size) as the Independent Variable
```{r, echo=FALSE}
rev_mark <- lm(revenue ~ marketsize, data = mnc)
summary(rev_mark)
ggplot(data = mnc, aes(x = marketsize, y = revenue)) + geom_point() + geom_smooth(method='lm',formula = y~x)

```
The market size variable has a positive inpact on revenue. The estimate of market size tells us that 1 % change in market size will result in 0.46 % change in revenue. The p-value is less than 0.05 and is significant on a 5 % level, and the revenue variable is described by 9.4 % in this model.

#### 4.3.2.3 `relationship` (Relationship with clients and suppliers) as the Independent Variable
```{r, echo=FALSE}
rev_rel <- lm(revenue ~ relationship, data = mnc)
summary(rev_rel)

```
Relationship has a positive inpact on revenue. By increasing the number of relationships by one, revenue will increase by 19.5 %, holding all other variables constant. The p-value is less than 0.05 and it is significant on a 5 % level, and the revenue variable is described by 7.5 % in this model.

#### 4.3.2.4 `licenses` (Licenses) as the Independent Variable
```{r}
rev_lic <- lm(revenue ~ licenses, data = mnc)
summary(rev_lic)

```
Licenses has a positive inpact on revenue. The estimate of licenses tells us that 1 % change in licenses will result in 0.36 % change in revenue. The p-value is less than 0.05 and it is significant on a 5 % level. However, the revenue variable is described by only 1.6 % in this model. In this case, we would not include this factor when doing the multiple linear regression test.

#### 4.3.2.5 `lceopay` (Log of the CEO pay) as the Independent Variable
```{r}
rev_ceo <- lm(revenue ~ lceopay, data = mnc)
summary(rev_ceo)
ggplot(data = mnc, aes(x = lceopay, y = revenue)) + geom_point(na.rm = TRUE) + geom_smooth(method='lm',formula = y~x, na.rm = TRUE)

```

#### 4.3.2.6 `lceopay` (Log of the CEO pay) as the Independent Variable with Different Ownership Structure
```{r}
library(ggplot2)
ggplot(data = mnc, aes(x = lceopay, y = revenue)) + geom_point(alpha = 1/2, na.rm = TRUE) + theme_minimal() + geom_smooth(aes(col = ownership), method = 'lm')

```

The CEO pay (lceopay) has a positive inpact on revenue. The estimate of lceopay tells us that 1 % change in the CEO pay will result in 0.9 % change in revenue. The p-value is less than 0.05 and is significant on a 5 % level, and the revenue variable is described by 24.3 % in this model.

### 4.3.3 Multiple Linear Regression Test with `Revenue` as the Dependent Variable

As a result of our correlation analysis and single regression models we would like to look further into the revenue variable by adding relationship, marketsize, CEO pay, number of employees and GDP per capita in 2003 as independent variables.  

```{r, tidy = TRUE, results='hide'}
rev_reg1 <- lm(revenue ~ lceopay + relationship + marketsize + lgdpper2003 + lemp + letcs, data = mnc)
summary(rev_reg1)
ggplot(data = mnc, aes(x = lceopay+relationship+marketsize+lgdpper2003+lemp+letcs, y = revenue)) + geom_point(na.rm = TRUE) + geom_smooth(method='lm',formula = y~x, na.rm = TRUE)

```

```{r, results = 'asis', tidy = TRUE}

```

From this regression model we get an adjusted R-squared equal to 0.72, which means that 72% of the revenue variable is described in this model. All the dependent variables are significant at the 1% level, except for lgdpper2003 which is significant at the 5 % level. 

The intercept of -0.30 tells us what the log of revenue will be if all our independent variables are zero. This number is negative and does not give us any valuable information without combining it with more variables. 

If we look at the relationship variable we can see that by increasing the number of relationships by one, revenue will increase by 13.6 %. The estimate of marketsize tells us that 1 % change in marketsize will result in 0.31 % change in revenue. By looking at the lceopay we can see that 1 % change in the CEO pay will result in 0.76 % change in revenue. The estimate of lgdpper2003 tells us that an increase in GDP per capita of 1 % will decrease revenue by 0.08 %. 

# REMEMBER!!! --- An

### 4.3.1. Multiple Linear Regression with `lgdpper2003` (GDP per capita in 2003 (log)) as Dependent Variable

```{r, echo=FALSE} 
panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- abs(cor(x, y))
    txt <- format(c(r, 0.123456789), digits = digits)[1]
    txt <- paste0(prefix, txt)
    if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex = cex.cor * r)
}
pairs(lgdpper2003 ~ lwdist + lpop2003 + MNC, data = mnc.prov, lower.panel = panel.smooth, upper.panel = panel.cor)


#linear regression 
lm_gdp2003 <- lm(lgdpper2003 ~ lwdist + MNC , data = mnc.prov)
summary(lm_gdp2003)

```

We can find out that the Adjusted R-squared is 0.6831, and we got the linear regression model function that:
$$lgdpper2003 = 8.27 - 0.44*lwdist + 0.49*MNC $$

# REMEMBER!!! --- Kaixuan, more comment before and after the code

# 5. Discussion and Conclusion
## 5.1 Discussion
Based on the past reports, the performance of one company is believed to have strong relationship with its connection to the government. Since Chinese government has a strong interception on its country's economy, and many companies in China are state-owned, we wanted to check whether the revenue of one company is correlated with the governmental factors.

However, in our correlation analysis about the dataset, we could not find any strong correlation between the company's revenue and governmental factors. Therefore, we went further to search for other factors that might have influence on the performance of the company. Beyond this, we found some interesting variables in the dataset that have strong correlation with the company's revenue.

Factors like the payment for CEO, the number of relationship with clients and suppliers, the market size, the GDP per capita, the number of employee and the expenses on the entertainment have an obvious impact on the performance of the company with a high explanation (72%) of the varibility of the revenue change. We also found that different type of ownership resulted in a mixed impact on the revenue change. Being owned by the state did not immdediately give a company significant advantage.

Moreover, there was a negative correlation between entertainment expenditures and revenue. The variable that Zhu (2015) believed to be an indicator of political relationship and potential corrupt practices does not necessarily improve financial performance. The limitation could be, high entertainment expenditures in a particular year is a process of relationship building. The implication could take time. Moreover, there is no records of entertainment expenditures from previous years in this dataset, which could possibly illustrate the connection better.


Other things we discovered in this analysis are:

The MNC activity and GDP per capita has a high positive correlation, which indicates that FDI (foreign direct investment) could stimulate the economy of China.

Around 73.8 per cent of companies in the sample is owned by a mix of foreign investors, private and government. None of them held more than 50 per cent of the shares. The number of private owned companies are surprisingly very small and their average revenue is lower than the other firms.



# References
Hlavac, M. (2015). *stargazer: Well-Formatted Regression and Summary Statistics Tables*. R package version 5.2. http://CRAN.R-project.org/package=stargazer  
You, J. & Du, G. (2012). Are Political Connections a Blessing or a Curse? Evidence from CEO Turnover in China, *Corporate Governance: An International Review*, 20(2). Accessed through: EBSCOHost.  
Zhu, B. (2016). *Replication Data for: MNCs, Rents, and Corruption: Evidence from China*, doi:10.7910/DVN/VT4KJA, Harvard Dataverse, V1 [UNF:6:LTJM6CHylp/JU5AfkjBK8Q==]  
